18Q4

### 2019-04-26 18Q4.Rmd
updated 18Q4.Rmd for clarity

```{r, warning=FALSE}
crispr_pearson_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
                         summarize(p = cor.test(y = Score, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                                   corr = cor.test(y = Score, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                                   Metric = "Gene Expression")
crispr_pearson_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
                         summarize(p = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs")$p.value,
                                   corr = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs")$estimate,
                                   Metric = "Copy Number")
crispr_spearman_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
                          summarize(p = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                                    corr = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                                    Metric = "Gene Expression")
crispr_spearman_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
                          summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value,
                                    corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
                                    Metric = "Copy Number")
```

>>>>

```{r, warning=FALSE}
crispr_pearson_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>% summarize(p = cor.test(y = Score, x = RPKM, method = "pearson", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Metric = "Gene Expression")
crispr_pearson_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>% summarize(p = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs")$estimate, Metric = "Copy Number")
crispr_spearman_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%summarize(p = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression")
crispr_spearman_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number")
```
